Equalizer 2.0\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
More data compression results
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@28 db7c848b-7755-4df2-b763-8796797afa52

@@

>>>>

To benchmark the data distribution we used two datasets: The david statue at 2mm
resolution (\fig{fDavid2mm}) and 3D volumes of a spike frequencies of a 3
million neuron simulation (\fig{fVolumes}).

\begin{figure}[ht]\center
  \includegraphics[width=.49\columnwidth]{images/spikes512}\hfil
  \includegraphics[width=.49\columnwidth]{images/spikes1280}
  \caption{\label{fVolumes}Spike frequencies of a 3 million neuron simulation at
    437x240x512 (51MB, left) and 1092x600x1280 (800MB, right) resolution}
\end{figure}

The spike frequency volumes aggregate the number of spikes which happened within
a given voxel over a given time. The absolute spike count is renormalized to an
unsigned byte value (0..255) during creation. Higher densities in the volume
represent higher spiking activity in the voxel. Consequently, the volume is more
sparsely populated and has a more even distribution of values at higher
resolution.

@@

The compression ratio for the models used in the following benchmark deviate
from this averaged distribution. \fig{fCompressorDetail} shows the compression
ratios for the triangle and volume data.

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/compressorDetail}
  \caption{\label{fCompressorDetail}Data Compression for ply data (left, David
    statue 2mm) and raw volume data shown in \fig{fVolumes} (middle and right)}
\end{figure*}

The ply data is little compressible, the default compressor achieves a 10\%
reduction. This is due to a high entropy in the data and the dominant use of
floating point representations. Overall the profile is similar to the generic
benchmark, at a smaller compression rate.

The volume data on the other hand is sparsely populated and using integer (byte)
representation, which is easier to compress. The naive RLE implementation
already achieves a good compression, showing that the smaller volume contains at
most 28\% empty space and the bigger volume at most 90\%. Snappy and ZStandard
can reduce the data much further, reducing the data to a few megabytes.
